### 2020-01-10 paper/paper.tex
intro notes

Here we propose to simplify and improve calibration programs for
\eprv\ hardware systems with two very simple but novel ideas.
The first flows from the observation that calibration sources---which
include lamps, etalons, and laser-frequency combs (\lfc
s)---illuminate the spectrograph with dense sets of lines; almost every
location in the spectrograph image plane is surrounded by nearby,
useful calibration lines.
This recommends a calibration methodology that is
\emph{non-parametric}:
If every point in the spectrograph detector is surrounded by nearby
calibration lines, the wavelength solution can be made simply an
interpolation of the calibration data.
There is no need to choose any functional form for the wavelength
solution, such as an eighth-order polynomial.
Going non-parametric will improve calibration accuracy, because
choosing a parametric form biases the calibration, and biases it
badly when the form is inappropriate.

@@

>>>>

Here we propose to simplify and improve calibration programs for
\eprv\ hardware systems with two very simple but novel ideas.
The first flows from the observation that calibration sources---which
include lamps, etalons, and laser-frequency combs (\lfc
s)---illuminate the spectrograph with dense sets of lines; almost every
location in the spectrograph image plane is surrounded by nearby,
useful calibration lines.
This recommends a calibration methodology that is
\emph{non-parametric}:
If every point in the spectrograph detector is surrounded by nearby
calibration lines, the wavelength solution can be made simply an
interpolation of the calibration data.
There is no need to choose any functional form for the wavelength
solution, such as an eighth-order polynomial.
Going non-parametric will improve calibration accuracy, because
choosing a parametric form biases the calibration, and biases it
badly when the form is inappropriate (as, for example, polynomials
will be at the detector edges).

@@

HOGG: Return to the point that non-parametric \emph{increases} the
freedom of the model (infinitely in some sense) but hierarchical
\emph{restricts} the freedom of the model (enormously, but we hope
appropriately).... HOGG
